### 2021-06-04 memo.tex
explicit bordism invariants

@@

>>>>

The corresponding invariant in 4d is simply \begin{equation}
\exp(2\pi i \frac{p}{4} \int \frac12\mathfrak{P}(a) )
\end{equation}
where $\mathfrak{P}:H^2(-,\bZ_4)\to H^4(-,\bZ_8)$ is the Pontryagin square,
which is even mod 8 on a spin manifold.

@@

The corresponding bordism invariants in 4d are $\mathfrak{P}(a)/2$, $ab$, $\mathfrak{P}(b)/2$, 
and the one in 5d is $a\beta b$.
